Replacing hand-written signatures with open electronic signature software

### 2020-01-28 paper/main.tex
Edit bibliography
Update footnote link

\title{Open electronic signature software}
\author{Jakub Ďuraš}
\typprace{bachelor's}
\rok{2020}
\odbor{Applied Informatics}
\miesto{Košice}
\podakovanie{
  Thanks to the Planet!
}
\veduci{RNDr. Viliam Kačala}
\pracovisko{Institute of Computer Science}
\pdfzadanie{zadanie.pdf}

@@

Qualified electronic signatures (QES) are a subset of advanced electronic signatures with more specific requirements that can be found in the annex 1 of the eIDAS regulation\footnote{https://eur-lex.europa.eu/legal-content/EN/TXT/HTML/?uri=CELEX:32014R0910\#d1e32-111-1}.
In more practical terms, such advanced electronic signatures are created with a qualified device using a qualified certificate and a qualified trust service. Qualified in this case means authorized for such use by the legal authorities.

>>>>

\title{Replacing hand-written signatures with open electronic signature software}
\author{Jakub Ďuraš}
\typprace{bachelor's}
\rok{2020}
\odbor{Applied Informatics}
\miesto{Košice}
\podakovanie{
  Thanks to the Planet!
}
\veduci{RNDr. Viliam Kačala}
\pracovisko{Institute of Computer Science}
\pdfzadanie{zadanie.pdf}

@@

Qualified electronic signatures (QES) are a subset of advanced electronic signatures with more specific requirements that can be found in the annex 1 of the eIDAS regulation\footnote{Available at https://eur-lex.europa.eu/legal-content/EN/TXT/HTML/?uri=CELEX:32014R0910\#d1e32-111-1}.
In more practical terms, such advanced electronic signatures are created with a qualified device using a qualified certificate and a qualified trust service. Qualified in this case means authorized for such use by the legal authorities.
